---
title: "NFL Matchup Digest"
subtitle: "Season `r params$season`, Week `r params$week`"
output:
  html_document:
    self_contained: false   # see Note on file size below
    toc: false
params:
  season: 2026
  week: 2
  hvt_yardline: 10
  matchup_filter: "ALL"   # "ALL" renders every game in this week's slate.
                            # Set to a single team abbreviation (e.g. "KC") to
                            # render just that team's game — useful for
                            # spot-checking one card without regenerating
                            # the whole slate.
---

<!--
NOTE on self_contained: false (changed from true)
Pandoc's --self-contained mode scans the ENTIRE rendered document for <img>,
<video>, etc. — including plain raw HTML tags like the headshot/logo <img>
tags built by glue() below, not just markdown-native images — and fetches +
base64-embeds every one it finds, local or remote. With ~16 games x ~16
images each (logos + headshots), that's 250+ remote fetches baked into one
file, which is what caused both the slow RPubs publish and the "413 Request
Entity Too Large" error. With self_contained: false, those <img src="https://...">
tags stay as plain links instead — the file stays small, but knitting now
also writes a small NFL_Matchup_Digest_files/ folder alongside the .html
(the template's own CSS/JS, not our images — those never needed embedding).
Keep that folder together with the .html when moving/uploading it manually;
rsconnect::rpubsUpload() and RStudio's Publish button both handle this
automatically and don't need special handling.
-->

<style>
body { font-family: -apple-system, "Segoe UI", Helvetica, Arial, sans-serif; color: #1a1a1a; max-width: 900px; margin: 0 auto; }
h1.title, h2.subtitle { text-align: center; }

.matchup-card { margin: 0 0 70px 0; }
@media print {
  .matchup-card { page-break-after: always; }
}

.matchup-header {
  display: flex; align-items: center; justify-content: center; gap: 36px;
  padding: 22px 10px; border-radius: 14px; margin-bottom: 18px;
}
.team-block { text-align: center; width: 180px; }
.team-block img.logo { height: 76px; }
.team-name { font-size: 1.25em; font-weight: 800; margin-top: 6px; letter-spacing: 0.3px; }
.team-record { font-size: 0.95em; opacity: 0.85; font-weight: 600; }
.at-symbol { font-size: 1.8em; font-weight: 300; color: #ffffffcc; }

.compare-table { width: 100%; border-collapse: collapse; margin: 10px 0 26px 0; }
.compare-table td { padding: 7px 10px; border: none; font-size: 0.95em; }
.compare-table tr:nth-child(even) { background: #f6f6f8; }
.compare-table .away-val, .compare-table .home-val {
  width: 24%; font-weight: 700; font-size: 1.02em;
}
.compare-table .away-val { text-align: right; }
.compare-table .home-val { text-align: left; }
.compare-table .stat-label {
  width: 52%; text-align: center; color: #666; font-size: 0.82em;
  text-transform: uppercase; letter-spacing: 0.6px;
}

.section-heading {
  font-size: 1.05em; font-weight: 800; text-transform: uppercase; letter-spacing: 0.8px;
  padding: 6px 14px; border-radius: 6px; color: white; margin: 22px 0 10px 0;
}

.pos-columns { display: flex; gap: 26px; margin-bottom: 8px; }
.pos-col { flex: 1; min-width: 0; }

.player-card {
  display: flex; align-items: center; gap: 10px; padding: 8px 6px;
  border-bottom: 1px solid #eee;
}
.player-card img.headshot {
  width: 42px; height: 42px; border-radius: 50%; object-fit: cover;
  background: #ddd; flex-shrink: 0;
}
.player-info { flex: 1; min-width: 0; }
.player-name { font-weight: 700; font-size: 0.92em; }
.player-team { font-size: 0.75em; color: #888; }
.player-stats { font-size: 0.78em; color: #444; line-height: 1.5; margin-top: 2px; }
.player-stats b { color: #111; }

.def-table { width: 100%; border-collapse: collapse; font-size: 0.85em; margin-bottom: 10px; }
.def-table th { text-align: left; color: #888; font-weight: 600; text-transform: uppercase; font-size: 0.75em; padding: 4px 8px; }
.def-table td { padding: 4px 8px; border-top: 1px solid #eee; }
.def-table tr:nth-child(even) td { background: #f9f9fa; }
.def-table img.headshot { width: 26px; height: 26px; vertical-align: middle; margin-right: 6px; }

.st-line { font-size: 0.88em; padding: 4px 0; }
.st-line b { display: inline-block; width: 46%; }
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

library(nflreadr)
library(dplyr)
library(tidyr)
library(stringr)
library(purrr)
library(glue)

# Persist downloaded nflverse data to disk between knits (default is
# "memory", which only caches within a single R session — so every fresh
# knit re-downloads everything from scratch over the network). This matters
# most here: this document alone calls load_pbp(), load_player_stats() x2,
# load_nextgen_stats() x3, load_espn_qbr(), load_ftn_charting(), and
# load_teams() — seven-plus separate network downloads every knit without
# this. First knit each week is still a real download; every knit after
# that reuses the cached files instead of re-fetching.
options(nflreadr.cache = "filesystem")

season <- params$season
week   <- params$week
```

```{r load-core-data}
# Core datasets. NGS/QBR here are SEASON-TO-DATE THROUGH params$week (not a
# single week), so they use the same weighted-mean-before-overwrite pattern
# as the Range Digest, treating "week 1 through week X" as the range.
pbp        <- load_pbp(seasons = season)
schedules  <- load_schedules(seasons = season)
player_wk  <- load_player_stats(seasons = season, stat_type = "offense")
player_def <- load_player_stats(seasons = season, stat_type = "defense")
team_info  <- load_teams(current = TRUE) |>
  select(team_abbr, team_name, team_color, team_color2, team_logo_espn)

pbp_ytd <- pbp |> filter(week <= !!week)

ftn_charting <- tryCatch(
  # Load the full charting table, not a trimmed-down select() of it — this
  # object may be reused by other chunks (see below) that need different
  # columns (e.g. is_play_action, read_thrown). Narrowing it here once would
  # silently break any chunk added later that needs a column this one drops.
  load_ftn_charting(seasons = season),
  error = function(e) NULL
)

ngs_passing <- tryCatch({
  load_nextgen_stats(seasons = season, stat_type = "passing") |>
    filter(week >= 1, week <= !!week, week != 0) |>
    mutate(team_abbr = clean_team_abbrs(team_abbr)) |>
    group_by(player_gsis_id, player_display_name, team_abbr) |>
    summarise(
      avg_time_to_throw = weighted.mean(avg_time_to_throw, w = attempts, na.rm = TRUE),
      completion_percentage_above_expectation = weighted.mean(completion_percentage_above_expectation, w = attempts, na.rm = TRUE),
      attempts = sum(attempts, na.rm = TRUE),
      .groups = "drop"
    )
}, error = function(e) NULL)

ngs_rushing <- tryCatch({
  load_nextgen_stats(seasons = season, stat_type = "rushing") |>
    filter(week >= 1, week <= !!week, week != 0) |>
    mutate(team_abbr = clean_team_abbrs(team_abbr)) |>
    group_by(player_gsis_id, player_display_name, team_abbr) |>
    summarise(
      rush_yards_over_expected_per_att = weighted.mean(rush_yards_over_expected_per_att, w = rush_attempts, na.rm = TRUE),
      percent_attempts_gte_eight_defenders = weighted.mean(percent_attempts_gte_eight_defenders, w = rush_attempts, na.rm = TRUE),
      rush_yards_over_expected = sum(rush_yards_over_expected, na.rm = TRUE),
      rush_attempts = sum(rush_attempts, na.rm = TRUE),
      .groups = "drop"
    )
}, error = function(e) NULL)

ngs_receiving <- tryCatch({
  load_nextgen_stats(seasons = season, stat_type = "receiving") |>
    filter(week >= 1, week <= !!week, week != 0) |>
    mutate(team_abbr = clean_team_abbrs(team_abbr)) |>
    group_by(player_gsis_id, player_display_name, team_abbr) |>
    summarise(
      avg_separation = weighted.mean(avg_separation, w = targets, na.rm = TRUE),
      targets = sum(targets, na.rm = TRUE),
      .groups = "drop"
    )
}, error = function(e) NULL)

espn_qbr <- tryCatch({
  load_espn_qbr(seasons = season, summary_type = "week") |>
    filter(game_week >= 1, game_week <= !!week) |>
    mutate(team_abb = clean_team_abbrs(team_abb)) |>
    group_by(team_abb) |>
    summarise(qbr_total = weighted.mean(qbr_total, w = qb_plays, na.rm = TRUE), .groups = "drop")
}, error = function(e) NULL)
```

```{r team-level-stats}
# ---------------------------------------------------------------------------
# One 32-row table of every comparison-table stat, computed once and sliced
# per matchup below. Reuses the same logic already validated in the Weekly/
# Range Digests (standings, Quality Record, explosive plays, penalties,
# turnovers, 3-and-outs) rather than re-deriving it from scratch.
# ---------------------------------------------------------------------------
standings_long <- schedules |>
  filter(!is.na(result), week <= !!week) |>
  select(week, home_team, away_team, home_score, away_score) |>
  pivot_longer(cols = c(home_team, away_team), names_to = "side", values_to = "team") |>
  mutate(
    pf = if_else(side == "home_team", home_score, away_score),
    pa = if_else(side == "home_team", away_score, home_score),
    win = as.numeric(pf > pa), loss = as.numeric(pf < pa), tie = as.numeric(pf == pa)
  )

standings_summary <- standings_long |>
  group_by(team) |>
  summarise(W = sum(win), L = sum(loss), PF = sum(pf), PA = sum(pa), .groups = "drop")

team_streak <- standings_long |>
  arrange(team, week) |>
  group_by(team) |>
  summarise(
    streak = {
      res <- rev(case_when(win == 1 ~ "W", loss == 1 ~ "L", TRUE ~ "T"))
      if (length(res) == 0) {
        "-"
      } else {
        cur <- res[1]; n <- 1; i <- 2
        while (i <= length(res) && res[i] == cur) { n <- n + 1; i <- i + 1 }
        paste0(cur, n)
      }
    },
    .groups = "drop"
  )

# Quality Record (unchanged from Weekly/Range Digest logic)
qr_games <- schedules |> filter(!is.na(result), !is.na(spread_line), week <= !!week)
qr_home <- qr_games |> transmute(team = home_team, is_favorite = spread_line > 0, is_dog = spread_line < 0,
                                  pick_em = spread_line == 0, margin = result, line = spread_line,
                                  pushed = margin == line, covered = margin > line, won_outright = margin > 0)
qr_away <- qr_games |> transmute(team = away_team, is_favorite = spread_line < 0, is_dog = spread_line > 0,
                                  pick_em = spread_line == 0, margin = -result, line = -spread_line,
                                  pushed = margin == line, covered = margin > line, won_outright = margin > 0)
quality_record <- bind_rows(qr_home, qr_away) |>
  mutate(qr_result = case_when(
    pick_em ~ NA_character_, is_favorite & pushed ~ NA_character_,
    is_favorite & covered ~ "W", is_favorite & !covered ~ "L",
    is_dog & won_outright ~ "W", is_dog & !won_outright ~ NA_character_, TRUE ~ NA_character_
  )) |>
  group_by(team) |>
  summarise(QR_W = sum(qr_result == "W", na.rm = TRUE), QR_L = sum(qr_result == "L", na.rm = TRUE), .groups = "drop")

third_down <- pbp_ytd |>
  filter(down == 3, !is.na(posteam)) |>
  group_by(team = posteam) |>
  summarise(third_down_pct = mean(third_down_converted == 1, na.rm = TRUE), .groups = "drop")

drive_summary <- pbp_ytd |>
  filter(!is.na(fixed_drive), !is.na(posteam), !is.na(defteam)) |>
  group_by(game_id, fixed_drive, posteam, defteam) |>
  summarise(scrimmage_plays = sum(rush == 1 | pass == 1, na.rm = TRUE),
            drive_result = dplyr::first(na.omit(fixed_drive_result)), .groups = "drop")
own_3rd_out <- drive_summary |>
  filter(scrimmage_plays <= 3, str_detect(drive_result, regex("^punt", ignore_case = TRUE))) |>
  count(team = posteam, name = "three_and_outs")

exp_flagged <- pbp_ytd |>
  mutate(explosive_run = rush == 1 & yards_gained >= 10,
         explosive_pass = pass == 1 & complete_pass == 1 & yards_gained >= 20)
exp_for <- exp_flagged |> group_by(team = posteam) |>
  summarise(exp_run_for = sum(explosive_run, na.rm = TRUE), exp_pass_for = sum(explosive_pass, na.rm = TRUE), .groups = "drop")
exp_against <- exp_flagged |> group_by(team = defteam) |>
  summarise(exp_run_allow = sum(explosive_run, na.rm = TRUE), exp_pass_allow = sum(explosive_pass, na.rm = TRUE), .groups = "drop")

box_avg <- tibble(team = character(), avg_defenders_in_box = double())
if (!is.null(ftn_charting)) {
  box_avg <- ftn_charting |>
    inner_join(pbp_ytd |> filter(rush == 1) |> select(game_id, play_id, defteam),
               by = c("nflverse_game_id" = "game_id", "nflverse_play_id" = "play_id")) |>
    filter(!is.na(n_defense_box)) |>
    group_by(team = defteam) |>
    summarise(avg_defenders_in_box = mean(n_defense_box, na.rm = TRUE), .groups = "drop")
}

off_plays <- pbp_ytd |> filter(rush == 1 | pass == 1)
off_yards <- off_plays |> group_by(team = posteam) |> summarise(off_yards = sum(yards_gained, na.rm = TRUE), .groups = "drop")
def_yards <- off_plays |> group_by(team = defteam) |> summarise(def_yards = sum(yards_gained, na.rm = TRUE), .groups = "drop")

penalty_flagged <- pbp_ytd |> filter(penalty == 1, !is.na(penalty_team), !is.na(posteam), !is.na(defteam))
pen_committed <- penalty_flagged |> filter(penalty_team == posteam | penalty_team == defteam) |>
  mutate(team = penalty_team) |> count(team, name = "penalties_against")
pen_drawn <- penalty_flagged |>
  mutate(team = if_else(penalty_team == posteam, defteam, posteam)) |>
  count(team, name = "penalties_for")

takeaways <- pbp_ytd |> group_by(team = defteam) |>
  summarise(takeaways = sum(interception == 1 | fumble_lost == 1, na.rm = TRUE), .groups = "drop")
giveaways <- pbp_ytd |> group_by(team = posteam) |>
  summarise(giveaways = sum(interception == 1 | fumble_lost == 1, na.rm = TRUE), .groups = "drop")

punts <- pbp_ytd |> filter(play_type == "punt") |> count(team = posteam, name = "punts")

drive_start <- pbp_ytd |>
  filter(!is.na(fixed_drive), !is.na(posteam)) |>
  group_by(game_id, fixed_drive, posteam) |>
  slice_min(play_id, n = 1, with_ties = FALSE) |>
  ungroup() |>
  select(team = posteam, drive_start_transition, yardline_100)
kickoff_start <- drive_start |> filter(str_detect(drive_start_transition, regex("kickoff", ignore_case = TRUE))) |>
  group_by(team) |> summarise(avg_start_kickoff = mean(100 - yardline_100, na.rm = TRUE), .groups = "drop")
punt_return_start <- drive_start |> filter(str_detect(drive_start_transition, regex("^punt", ignore_case = TRUE))) |>
  group_by(team) |> summarise(avg_start_punt = mean(100 - yardline_100, na.rm = TRUE), .groups = "drop")

team_matchup_stats <- tibble(team = team_info$team_abbr) |>
  left_join(standings_summary, by = "team") |>
  left_join(team_streak, by = "team") |>
  left_join(quality_record, by = "team") |>
  left_join(third_down, by = "team") |>
  left_join(own_3rd_out, by = "team") |>
  left_join(exp_for, by = "team") |>
  left_join(exp_against, by = "team") |>
  left_join(box_avg, by = "team") |>
  left_join(off_yards, by = "team") |>
  left_join(def_yards, by = "team") |>
  left_join(pen_committed, by = "team") |>
  left_join(pen_drawn, by = "team") |>
  left_join(takeaways, by = "team") |>
  left_join(giveaways, by = "team") |>
  left_join(punts, by = "team") |>
  left_join(kickoff_start, by = "team") |>
  left_join(punt_return_start, by = "team") |>
  mutate(across(c(W, L, QR_W, QR_L, third_down_pct, three_and_outs, exp_run_for, exp_pass_for,
                  exp_run_allow, exp_pass_allow, off_yards, def_yards, penalties_against,
                  penalties_for, takeaways, giveaways, punts), ~replace_na(., 0)),
         streak = replace_na(streak, "-"),
         to_ratio = takeaways / pmax(giveaways, 1))
```

```{r player-level-stats}
# ---------------------------------------------------------------------------
# Season-to-date-through-week leaders per team, one row per player, with
# NGS/HVT columns merged in. "Top" = most volume (attempts/carries/targets).
# ---------------------------------------------------------------------------
qb_season <- player_wk |>
  filter(week <= !!week, position == "QB") |>
  group_by(player_id, player_display_name, team) |>
  summarise(attempts = sum(attempts, na.rm = TRUE), passing_tds = sum(passing_tds, na.rm = TRUE),
            passing_interceptions = sum(passing_interceptions, na.rm = TRUE),
            passing_epa = sum(passing_epa, na.rm = TRUE),
            headshot_url = dplyr::first(headshot_url), .groups = "drop") |>
  filter(attempts >= 5) |>
  left_join(ngs_passing |> select(player_gsis_id, completion_percentage_above_expectation),
            by = c("player_id" = "player_gsis_id")) |>
  left_join(espn_qbr, by = c("team" = "team_abb")) |>
  group_by(team) |> slice_max(attempts, n = 1, with_ties = FALSE) |> ungroup()

hvt_touches <- pbp_ytd |>
  filter(rush == 1, yardline_100 <= params$hvt_yardline, !is.na(rusher_player_id)) |>
  group_by(player_id = rusher_player_id) |>
  summarise(hvt_touches = n(), hvt_touch_tds = sum(rush_touchdown, na.rm = TRUE), .groups = "drop")
hvt_targets <- pbp_ytd |>
  filter(pass == 1, yardline_100 <= params$hvt_yardline, !is.na(receiver_player_id)) |>
  group_by(player_id = receiver_player_id) |>
  summarise(hvt_targets = n(), hvt_target_tds = sum(pass_touchdown, na.rm = TRUE), .groups = "drop")

rb_season <- player_wk |>
  filter(week <= !!week, position == "RB") |>
  group_by(player_id, player_display_name, team) |>
  summarise(carries = sum(carries, na.rm = TRUE), rushing_yards = sum(rushing_yards, na.rm = TRUE),
            rushing_tds = sum(rushing_tds, na.rm = TRUE), rushing_epa = sum(rushing_epa, na.rm = TRUE),
            headshot_url = dplyr::first(headshot_url), .groups = "drop") |>
  filter(carries >= 3) |>
  mutate(epa_per_carry = rushing_epa / pmax(carries, 1)) |>
  left_join(ngs_rushing |> select(player_gsis_id, rush_yards_over_expected, percent_attempts_gte_eight_defenders),
            by = c("player_id" = "player_gsis_id")) |>
  left_join(hvt_touches, by = "player_id") |>
  mutate(across(c(hvt_touches, hvt_touch_tds), ~replace_na(., 0))) |>
  group_by(team) |> slice_max(rushing_yards, n = 2, with_ties = FALSE) |> ungroup()

rec_season <- player_wk |>
  filter(week <= !!week, position %in% c("WR", "TE")) |>
  group_by(player_id, player_display_name, team, position) |>
  summarise(targets = sum(targets, na.rm = TRUE), receptions = sum(receptions, na.rm = TRUE),
            receiving_yards = sum(receiving_yards, na.rm = TRUE), receiving_tds = sum(receiving_tds, na.rm = TRUE),
            receiving_epa = sum(receiving_epa, na.rm = TRUE), wopr = mean(wopr, na.rm = TRUE),
            headshot_url = dplyr::first(headshot_url), .groups = "drop") |>
  filter(targets >= 2) |>
  mutate(epa_per_catch = receiving_epa / pmax(receptions, 1)) |>
  left_join(ngs_receiving |> select(player_gsis_id, avg_separation), by = c("player_id" = "player_gsis_id")) |>
  left_join(hvt_targets, by = "player_id") |>
  mutate(across(c(hvt_targets, hvt_target_tds), ~replace_na(., 0)))

wr_season <- rec_season |> filter(position == "WR") |> group_by(team) |>
  slice_max(receiving_yards, n = 3, with_ties = FALSE) |> ungroup()
te_season <- rec_season |> filter(position == "TE") |> group_by(team) |>
  slice_max(receiving_yards, n = 2, with_ties = FALSE) |> ungroup()

def_season <- player_def |>
  filter(week <= !!week) |>
  group_by(player_id, player_display_name, team) |>
  summarise(def_tackles = sum(def_tackles_solo, na.rm = TRUE) + sum(def_tackles_with_assist, na.rm = TRUE),
            def_tackles_for_loss = sum(def_tackles_for_loss, na.rm = TRUE),
            def_sacks = sum(def_sacks, na.rm = TRUE), def_interceptions = sum(def_interceptions, na.rm = TRUE),
            def_pass_defended = sum(def_pass_defended, na.rm = TRUE),
            headshot_url = dplyr::first(headshot_url), .groups = "drop") |>
  group_by(team) |> slice_max(def_tackles, n = 3, with_ties = FALSE) |> ungroup()

team_sacks <- player_def |> filter(week <= !!week) |>
  group_by(team) |> summarise(team_sacks = sum(def_sacks, na.rm = TRUE), .groups = "drop")
```

```{r render-function}
# ---------------------------------------------------------------------------
# Builds the full HTML block for one matchup. Called once below for the
# prototype game; extends to loop over every game in week_games once approved.
# ---------------------------------------------------------------------------
fmt_pct <- function(x) sprintf("%.0f%%", 100 * x)
fmt1 <- function(x) sprintf("%.1f", x)
fmt2 <- function(x) sprintf("%.2f", x)
na_dash <- function(x) if (is.na(x) || is.null(x)) "-" else x

headshot_tag <- function(url, alt = "") {
  src <- if (is.na(url) || is.null(url) || url == "") "" else url
  glue('<img class="headshot" src="{src}" onerror="this.style.visibility=\'hidden\'" alt="{alt}">')
}

compare_row <- function(away_val, label, home_val) {
  glue('<tr><td class="away-val">{away_val}</td><td class="stat-label">{label}</td><td class="home-val">{home_val}</td></tr>')
}

section_heading <- function(text, color) {
  glue('<div class="section-heading" style="background:{color};">{text}</div>')
}

player_card <- function(name, team_abbr, headshot_url, stat_line) {
  glue('
  <div class="player-card">
    {headshot_tag(headshot_url, name)}
    <div class="player-info">
      <div class="player-name">{name}</div>
      <div class="player-team">{team_abbr}</div>
      <div class="player-stats">{stat_line}</div>
    </div>
  </div>')
}

render_matchup <- function(away, home) {
  away_info <- team_info |> filter(team_abbr == away)
  home_info <- team_info |> filter(team_abbr == home)
  a <- team_matchup_stats |> filter(team == away)
  h <- team_matchup_stats |> filter(team == home)

  header <- glue('
  <div class="matchup-header" style="background: linear-gradient(90deg, {away_info$team_color} 0%, {away_info$team_color} 45%, {home_info$team_color} 55%, {home_info$team_color} 100%);">
    <div class="team-block">
      <img class="logo" src="{away_info$team_logo_espn}">
      <div class="team-name" style="color:{away_info$team_color2};">{away_info$team_name}</div>
      <div class="team-record" style="color:{away_info$team_color2};">{a$W}-{a$L}</div>
    </div>
    <div class="at-symbol">@</div>
    <div class="team-block">
      <img class="logo" src="{home_info$team_logo_espn}">
      <div class="team-name" style="color:{home_info$team_color2};">{home_info$team_name}</div>
      <div class="team-record" style="color:{home_info$team_color2};">{h$W}-{h$L}</div>
    </div>
  </div>')

  compare <- paste0(
    '<table class="compare-table">',
    compare_row(glue("{a$W}-{a$L}"), "Win-Loss", glue("{h$W}-{h$L}")),
    compare_row(glue("{a$QR_W}-{a$QR_L}"), "Quality Win-Loss", glue("{h$QR_W}-{h$QR_L}")),
    compare_row(a$streak, "Current Streak", h$streak),
    compare_row(a$PF, "Points For", h$PF),
    compare_row(a$PA, "Points Against", h$PA),
    compare_row(fmt_pct(a$third_down_pct), "3rd Down %", fmt_pct(h$third_down_pct)),
    compare_row(a$three_and_outs, "3-and-Outs (Own Offense)", h$three_and_outs),
    compare_row(a$exp_run_for, "Explosive Runs For", h$exp_run_for),
    compare_row(a$exp_run_allow, "Explosive Runs Against", h$exp_run_allow),
    compare_row(fmt1(a$avg_defenders_in_box), "Avg Defenders in Box", fmt1(h$avg_defenders_in_box)),
    compare_row(a$exp_pass_for, "Explosive Pass Plays For", h$exp_pass_for),
    compare_row(a$exp_pass_allow, "Explosive Pass Plays Against", h$exp_pass_allow),
    compare_row(a$off_yards, "Total Yards Gained", h$off_yards),
    compare_row(a$def_yards, "Total Yards Allowed", h$def_yards),
    compare_row(a$penalties_against, "Penalties Against", h$penalties_against),
    compare_row(a$penalties_for, "Penalties For", h$penalties_for),
    compare_row(fmt2(a$to_ratio), "Takeaway/Giveaway Ratio", fmt2(h$to_ratio)),
    '</table>'
  )

  qb_block <- function(team_abbr, color) {
    q <- qb_season |> filter(team == team_abbr)
    if (nrow(q) == 0) return(section_heading(paste(team_abbr, "QB — no qualifying passer"), color))
    stat_line <- glue(
      "CPOE: <b>{fmt1(q$completion_percentage_above_expectation)}</b> &nbsp;|&nbsp; ",
      "TD: <b>{q$passing_tds}</b> &nbsp;|&nbsp; INT: <b>{q$passing_interceptions}</b><br>",
      "Dropback EPA: <b>{fmt1(q$passing_epa)}</b> &nbsp;|&nbsp; QBR: <b>{fmt1(q$qbr_total)}</b>"
    )
    player_card(q$player_display_name, team_abbr, q$headshot_url, stat_line)
  }

  rb_block <- function(team_abbr) {
    r <- rb_season |> filter(team == team_abbr)
    if (nrow(r) == 0) return("<i>No qualifying rushers</i>")
    paste(purrr::pmap_chr(r, function(...) {
      row <- list(...)
      stat_line <- glue(
        "RYOE: <b>{fmt1(row$rush_yards_over_expected)}</b> &nbsp;|&nbsp; ",
        "Stacked Box %: <b>{fmt_pct(row$percent_attempts_gte_eight_defenders/100)}</b><br>",
        "EPA/Carry: <b>{fmt2(row$epa_per_carry)}</b> &nbsp;|&nbsp; TD: <b>{row$rushing_tds}</b><br>",
        "HVT: <b>{row$hvt_touches}</b> &nbsp;|&nbsp; HVT TD: <b>{row$hvt_touch_tds}</b>"
      )
      player_card(row$player_display_name, team_abbr, row$headshot_url, stat_line)
    }), collapse = "")
  }

  rec_block <- function(df, team_abbr) {
    r <- df |> filter(team == team_abbr)
    if (nrow(r) == 0) return("<i>No qualifying receivers</i>")
    paste(purrr::pmap_chr(r, function(...) {
      row <- list(...)
      stat_line <- glue(
        "Tgt: <b>{row$targets}</b> &nbsp;|&nbsp; Yds: <b>{row$receiving_yards}</b> &nbsp;|&nbsp; TD: <b>{row$receiving_tds}</b><br>",
        "EPA/Catch: <b>{fmt2(row$epa_per_catch)}</b> &nbsp;|&nbsp; Sep: <b>{fmt1(row$avg_separation)}</b><br>",
        "WOPR: <b>{fmt2(row$wopr)}</b> &nbsp;|&nbsp; HVT: <b>{row$hvt_targets}</b> (TD: <b>{row$hvt_target_tds}</b>)"
      )
      player_card(row$player_display_name, team_abbr, row$headshot_url, stat_line)
    }), collapse = "")
  }

  def_block <- function(team_abbr) {
    d <- def_season |> filter(team == team_abbr)
    sacks <- team_sacks |> filter(team == team_abbr) |> pull(team_sacks)
    sacks_txt <- if (length(sacks) == 0) "0" else fmt1(sacks)
    rows <- if (nrow(d) == 0) {
      '<tr><td colspan="5"><i>No data</i></td></tr>'
    } else {
      paste(purrr::pmap_chr(d, function(...) {
        row <- list(...)
        glue('<tr><td>{headshot_tag(row$headshot_url, row$player_display_name)} {row$player_display_name}</td><td>{row$def_tackles}</td><td>{row$def_tackles_for_loss}</td><td>{row$def_sacks}</td><td>{row$def_interceptions}</td><td>{row$def_pass_defended}</td></tr>')
      }), collapse = "")
    }
    glue('
    <div><b>Team Sacks:</b> {sacks_txt}</div>
    <table class="def-table">
      <tr><th>Player</th><th>Tkl</th><th>TFL</th><th>Sk</th><th>INT</th><th>PBU</th></tr>
      {rows}
    </table>')
  }

  st_block <- function(team_abbr) {
    t <- team_matchup_stats |> filter(team == team_abbr)
    glue('
    <div class="st-line"><b>Punts</b> {t$punts}</div>
    <div class="st-line"><b>Avg Start (Kickoff)</b> Own {fmt1(t$avg_start_kickoff)}</div>
    <div class="st-line"><b>Avg Start (Punt Return)</b> Own {fmt1(t$avg_start_punt)}</div>')
  }

  qb_section <- glue('
  {section_heading("Quarterback", away_info$team_color)}
  <div class="pos-columns">
    <div class="pos-col">{qb_block(away, away_info$team_color)}</div>
    <div class="pos-col">{qb_block(home, home_info$team_color)}</div>
  </div>')

  rb_section <- glue('
  {section_heading("Running Backs", away_info$team_color)}
  <div class="pos-columns">
    <div class="pos-col">{rb_block(away)}</div>
    <div class="pos-col">{rb_block(home)}</div>
  </div>')

  wr_section <- glue('
  {section_heading("Wide Receivers", away_info$team_color)}
  <div class="pos-columns">
    <div class="pos-col">{rec_block(wr_season, away)}</div>
    <div class="pos-col">{rec_block(wr_season, home)}</div>
  </div>')

  te_section <- glue('
  {section_heading("Tight Ends", away_info$team_color)}
  <div class="pos-columns">
    <div class="pos-col">{rec_block(te_season, away)}</div>
    <div class="pos-col">{rec_block(te_season, home)}</div>
  </div>')

  def_section <- glue('
  {section_heading("Defense (Season Leaders by Tackles)", away_info$team_color)}
  <div class="pos-columns">
    <div class="pos-col">{def_block(away)}</div>
    <div class="pos-col">{def_block(home)}</div>
  </div>')

  st_section <- glue('
  {section_heading("Special Teams", away_info$team_color)}
  <div class="pos-columns">
    <div class="pos-col">{st_block(away)}</div>
    <div class="pos-col">{st_block(home)}</div>
  </div>')

  paste0(
    '<div class="matchup-card">',
    header, compare,
    qb_section, rb_section, wr_section, te_section, def_section, st_section,
    '</div>'
  )
}
```

```{r week-games}
week_games <- schedules |>
  filter(week == !!week, !is.na(home_team), !is.na(away_team)) |>
  select(game_id, away_team, home_team)

if (!identical(params$matchup_filter, "ALL")) {
  week_games <- week_games |>
    filter(away_team == params$matchup_filter | home_team == params$matchup_filter)
}
```

```{r clean-html-helper}
# Raw HTML built from nested glue()/paste0() calls easily ends up with a
# blank line or a line indented 4+ spaces somewhere inside it. Pandoc's
# markdown reader treats either as the signal to stop passing content
# through as raw HTML: a blank line closes the raw-HTML block outright, and
# a fresh line indented >=4 spaces gets read as an indented code block.
# Either one causes everything after it to render as literal escaped text
# instead of HTML. Strip both, once, per matchup, before emitting.
clean_html <- function(html_out) {
  html_out <- gsub("\n[ \t]*\n+", "\n", html_out)              # collapse blank lines
  html_out <- gsub("(?m)^[ \t]+", "", html_out, perl = TRUE)   # de-indent every line
  html_out
}
```

```{r render-all-matchups, results='asis'}
# Renders every game in week_games (or just one, if matchup_filter is set to
# a team abbreviation). Each card is cleaned independently before being
# joined, so one game's HTML quirks can't bleed into the next game's markup.
if (nrow(week_games) == 0) {
  cat(glue::glue("<p><i>No games found for Week {week} with the current matchup_filter (\"{params$matchup_filter}\"). Check the team abbreviation or that this week has been scheduled.</i></p>"))
} else {
  all_cards <- purrr::map2_chr(week_games$away_team, week_games$home_team, function(away, home) {
    clean_html(render_matchup(away, home))
  })
  cat(paste(all_cards, collapse = "\n"))
}
```

